\pisodm: Building SOC Applications in the Presence of Non-Functional Requirements

### 2017-11-23 JournalPISODM2016/FinalVersionNov2017/main.tex
no message

@@

\newcommand{\mm}[1]{\marginpar{\textcolor{magenta}{\textbf{Martin: }#1}}}
%\newcommand{\imartin}[1]{\textcolor{blue}{\textbf{Martin: }#1}}
%
%\newcommand{\umberto}[1]{\marginpar{\textcolor{orange}{\textbf{Umberto: }#1}}}
%\newcommand{\iumberto}[1]{\textcolor{orange}{\textbf{Umberto: }#1}}

@@

\def\BottomCatch{%
\vskip -10pt
\thispagestyle{empty}%
\begin{table}[b]%
\NINE\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr@{}}%
\\[-12pt]
Copyright \copyright\ 2017 Inderscience Enterprises Ltd. & &%
\end{tabular*}%
\vskip -30pt%
%%\vskip -35pt%
\end{table}%
}
\makeatother

@@

\authorC{\sf Javier~A.~Espinosa-Oviedo}
\affC{Barcelona Supercomputing Centre (BSC), Spain and
	French-Mexican Laboratory of Informatics and Automatic Control (LAFMIA), Mexico\\
  E-mail: javiera.espinosa@gmail.com}

@@

\authorG{\sf Genoveva~Vargas-Solar}
\affG{Univ. Grenoble Alpes, CNRS, Institute of Engineering Univ. Grenoble Alpes (Grenoble INP), LIG, 38000 Grenoble, France
	\\
  E-mail: genoveva.vargas@imag.fr}

\authorH{\sf Jos\'e-Luis~Zechinelli-Martini}
\affH{Universidad de las Am\'ericas-Puebla -- Cholula, Mexico and
	French-Mexican Laboratory of Informatics and Automatic Control (LAFMIA), Mexico\\
  E-mail: joseluis.zechinelli@udlap.mx}

@@

\REF{to this paper should be made as follows: Rodr\'{\i}guez
Khalid Belhajjame, Valeria~de~Castro, Javier~A.~Espinosa-Oviedo, Martin~A.~Musicante, Umberto~Souza~da~Costa, Pl\'acido~A.~Souza~Neto, Genoveva~Vargas-Solar, Jos\'e-Luis~Zechinelli-Martini (xxxx) `\pisodm: Building SOC Applications in the Presence of Non-Functional Requirements', {\it International Journal of Web and Grid Services}, Vol. x, No. x, pp.xxx\textendash xxx.}

\begin{bio}
Khalid Belhajjame is a lecturer (Maitre de Conférences) at the University Paris-Dauphine, where he is a member of the LAMSADE. His research interests lie in the areas of information and knowledge management. He has made key contributions to the areas of pay-as-you data integration, e-Science, scientific workflow management, provenance tracking and exploitation, and semantic web services.
\vs{9}

@@

\noindent Javier Alfonso Espinosa-Oviedo is a computer scientist specialized in the domains of databases and distributed systems. His research focus mainly on large-scale data management and processing based on service oriented architectures. He currently works as postdoctoral researcher at the Barcelona Supercomputing Centre (BSC), in the Extreme Computing Group, and is researcher at the French-Mexican Laboratory of Informatics and Automatic Control (LAFMIA), in the Database Management Group. His research interests include: Stream Processing, Urban Computing, Digital Humanities, Data Visualization. He has participated in several national and European projects (CASES EU-FP7; S2EUNET FP7-IRSES; POLIWEB PEPS CNRS), and has been invited as visiting researcher in different institutions (POLITO, Italy; UdelaR, Uruguay; NUAA, China; UDLAP, Mexico) where he has lectured on selected topics of data management.
\vs{9}

\noindent Martin A. Musicante received his B.Sc at ESLAI, Argentina, in 1988 and his M.Sc and PhD in Computer Science at Universidade Federal de Pernambuco, Brazil, in 1990 and 1996, respectively. He is full professor at Universidade Federal do Rio Grande do Norte-UFRN (Natal, Brazil). He is part of the graduate program in Computer Science at UFRN. Martin was associate researcher at LI - Université François Rabelais Tours (2002-2011) and at LIFO - Université d'Orléans, France, since 2008. 
\vs{9}

@@

\noindent Pl\'acido~A.~Souza~Neto received his B.Sc at CEFET-RN, Brazil, in 2005 and his M.Sc and PhD in Computer Science at Universidade Federal de Rio Grande do Norte, Brazil, in 2007 and 2012, respectively. He is an associate professor at Instituto Federal do Rio Grande do Norte-IFRN (Natal, Brazil). He was part of LIG (Grenoble - France) between 2014-2015 for as a post-doc fellow. He is part of the graduate program in Software Analysis and Development at IFRN. Plácido A. Souza Neto main current research topics are Software Engineering, Data Analysis, Model Driven Development and Web Services.
\vs{9}

@@

\noindent Jos\'e-Luis~Zechinelli-Martini is Associate professor of the Department of Computing, Electronics and Mecatronics at the Universidad de las Américas Puebla since 2002 and he is currently senior researcher at LAFMIA. He is head of the Data and Knowledge Management Group (DBKM) of LAFMIA. In 2001 he obtained his Ph.D. in Computer Science and in 1997 he obtained his Master Degree in Computer Science at University Joseph Fourier, Grenoble, France. In 1993 he obtained his diploma on Computer Systems Engineering at UDLAP. Between 2003 and 2006 he was director of the CENTIA y coordinator of the Ph.D program on Computer Science. His research project concerns on the integration of heterogeneous data services accessible in heterogeneous networks.
\end{bio}

@@

\begin{compactenum}[i]
\item To improve the development process by providing an abstract view of the application and helping to ensure the conformance to its specification.
\item To reduce the programming effort through the semi-automatic generation of  models for the application,  to produce concrete implementations from higher-level models.
\item To provide a general way of describing non-functional requirements.
\end{compactenum}

The applicability of our proposal was tested with an industrial case study concerning risk assessment for financial companies as implemented by the ORCA System\footnotemark \footnotetext{The ORCA System is a trademark of GCP Global (www.gcpglobal.com).}. In this work we show the application of our method \pisodm to develop a service based application called \FlyingPig that provides risk assessment as a service.
The models presented here were generated as a result of interacting with software developers at GCP Global and trying to fulfil  all the non-functional requirements present in the application.

@@

Despite of the different notations found in the literature for classifying NFRs, some NFRs are frequently considered, such as \textit{security}, \textit{performance}, \textit{reliability}, \textit{usability}, and \textit{availability}.
However, distinct hierarchies and models are proposed for NFRs, according to different perspectives.
We have identified a number of approaches~\cite{DAmbrogio06,CholletL09,SchmelingCM11,BasinDL06,Fabra2011,OvaskaEHPA10} that use MDD (Model Driven Development) for designing and developing applications.

@@

Figure~\ref{fig:CIM:usecasemetamodel} shows the \textit{$\pi$-UseCase} meta-model.
This model is  used to give the first representation of the application in terms of functionality, and of its non-func\-tion\-al requirements.
The notion of \textit{policy} is used to describe NFRs.
Figure~\ref{fig:CIM:usecasemetamodel} highlights the concepts related to NFRs.
The \textit{$\pi$-UseCase} meta-model extends the UML Use Case meta-model to describe NFRs with  the following  concepts:  \textsc{Business service}\footnotemark 
\mm{Small caps font does not appear as such!}\footnotetext{We use the 
{\sc small caps} font for referring to classes of a meta-model.}, {\sc End consumer}, {\sc Requirement}, {\sc Use Case}, {\sc Composite Use Case}, {\sc Non-\-Func\-tion\-al Requirement}, {\sc Non-Functional} {\sc At\-tri\-bute} and {\sc Constraint}.
An {\sc End Consumer} is represented by an {\sc Actor}.
An  {\sc Actor} is related to {\sc Use Cases} (from the original UML definition), as a {\sc  Composite Use Case} is a set of actions performed by the system which can be broken into different {\sc Use Cases}.
{\sc  Business Service} aggregates several {\sc Use Cases},  a service can be expressed by one or more use cases.
 The {\sc Business Collaborator} concept is represented  by {\sc Packages}.
A {\sc Business Collaborator} denotes an external service or a system that interacts with the application that is being modelled.
Each {\sc Business Collaborator} combines the features described in each  {\sc Package}.
%Thus, the service functions can be specified as being grouped into packages.

@@

\begin{example}[To Publish Music \textit{(cont)}]\label{ex:toPublicMusic3}
Considering the example scenario, the contract based process of activities  is shown in Figure~\ref{fig:CIM:serviceprocess}. The buy music and publish music services (update Twitter and Facebook) have pre- and post-conditions assertions that are composed into a contract for each service. The buy music pre-conditions consist in verifying:
\textit{(i)} if the User data are correct;
\textit{(ii)} if the User is already logged in Spotify;
\textit{(iii)} if bank account information are correct and;
\textit{(iv)} if there are enough funds in the bank account to cover the payment.
A post-condition ensures the complete transaction and verifies if a notification about the payment authorization was sent both to the user and to Spotify. 
There are four assertions for the buy music action, and each assertion has been detailed with the assertion property and predicate that must be verified. 
To update services, depending of each service, there may be different restrictions. As an example, a new verification of user data and message format is appropriate (maximum 140 characters), in the case of Twitter. In the case of Facebook, it is required that the user is already logged in Spotify and these data are the same as Facebook.
As post-condition, the application ensures that the Facebook service sends a notification of success.
To update Twitter a pre-condition is required, while to update Facebook it is necessary to check a pre-condition and a confirmation notice (modeled as post-condition).
As a pre-condition for ``twitter update'' it is necessary that (i) the music format is correct and (ii) the twitter login and password are correct for the update.
\end{example}

@@

\item The {\sc ServiceActivity} meta-class represents classes of composite activity types that must be carried out as part of a business service,  composed by  execu\-ta\-ble nodes.

@@

The relationships of type  {\sc Extend} and {\sc Include}  determine the way the business process is expressed as a workflow.  
The generated workflow is composed by {\sf Fork} and {\sf Join} nodes,  {\sc Control flow} constructors, as well as entities of type {\sc Action}.

@@

Figure~\ref{fig:E3valuemodel} shows the value model for the \FlyingPig\ application.
It is a business model that graphically represents a business case as a set of value exchanges ($\triangleright$ and $\triangleleft$) and value activities (rounded boxes) performed by business actors (squared boxes).
We identify two business actors: \textsl{ORCA} and \textsl{Broker}.
Brokers emit requests for risk assessment for one or more companies.
ORCA has two value activities which are services that provide an economical benefit:  \textsl{Identify Amendments} and \textsl{Assess Risk Situation}.
The values exchanged between ORCA and the brokers are:
\textit{(i)} \textsl{Questionnaire and Evidences} filled with information about the client company;
\textit{(ii)} \textsl{Amendments} which are ORCA's rec\-om\-men\-da\-tions, based on the data provided by the answers to questionnaires;
\textit{(iii)} \textsl{Evaluation Reports} for the client companies;
and
\textit{(iv)} the risk assessment \textsl{fee}.
%
The dependency path in Figure~\ref{fig:E3valuemodel} initiates with the need of assessment emitted by a particular company.
Once this need has been declared, the value exchanges between ORCA and Broker are triggered.
The client company provides ORCA with information (answers to a questionnaire), evidence (to support the information) and a fee (monetary value).
In the next step, ORCA suggests amendments (recommendations to change practices) and provides an evaluation report.

@@

Figure~\ref{fig:BPMNmodel} shows the BPMN model
for the \FlyingPig\ scenario. This model is partitioned for better understanding the value exchanging process.
The model includes two pools representing the \textsl{ORCA} system and the \textsl{Brokers}.
Brokers have two lanes, the client \textsl{Company} and a \textsl{User}.
The user is a contact member of the company, who  coordinates the assessment process.
This process  involves other members of the company as well.
%
The risk assessment process starts after a request from a company.
This corresponds to the value model, in which the start stimulus triggers the whole process.
The request leads to the definition of a group of users that will answer questionnaires to evaluate risk.
Other tasks include amending a ``risky situation'' as well as producing evidence to show that a specific risk has been eliminated\footnotemark \footnotetext{Risky situations include  material facts such as not facilitating access to physically disabled people in a bank agency or having an unsecured access to the premises of the company.
They can be also inmaterial restrictions such as the protocol used for accessing data on the company's computer server.}.

@@

\begin{compactenum}
\item An acknowledgement is due in less than 30 seconds after registering a task or demand for assessment.
\item The system should be able to deal with, at least, 200 users.
\item If the number of requests exceeds 200, \FlyingPig\ should implement a load balance strategy for processing the requests.
\item The privileges of the Channel-Broker must be verified \textit{before} the execution of the actions associated to the \textsf{designate user in charge} $\pi$-use case.
\item The privileges of users must be verified \textit{before} the execution of the actions associated to the \textsf{answer questionnaire and add evidences} $\pi$-use case.
\item All questionnaires need to be fully answered in order to consider a task as completed.
\item There is a time limit (in days) for amendments required by the system.
\end{compactenum}

@@

>>>>

\usepackage[T1]{fontenc}

@@

%\newcommand{\mm}[1]{\marginpar{\textcolor{magenta}{\textbf{Martin: }#1}}}
%\newcommand{\imartin}[1]{\textcolor{blue}{\textbf{Martin: }#1}}
%
%\newcommand{\umberto}[1]{\marginpar{\textcolor{orange}{\textbf{Umberto: }#1}}}
%\newcommand{\iumberto}[1]{\textcolor{orange}{\textbf{Umberto: }#1}}

@@

\def\BottomCatch{%
\vskip -10pt
\thispagestyle{empty}%
\begin{table}[b]%
\NINE\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr@{}}%
\\[-12pt]
Copyright \textcopyright\ 2017 Inderscience Enterprises Ltd. & &%
\end{tabular*}%
\vskip -30pt%
%%\vskip -35pt%
\end{table}%
}
\makeatother

@@

\authorC{\sf Javier~A.~Espinosa-Oviedo}
\affC{Barcelona Supercomputing Center (BSC), Spain and\\
	French-Mexican Laboratory of Informatics and Automatic Control (LAFMIA), Mexico/France\\
  E-mail: javiera.espinosa@bsc.es}

@@

\authorG{\sf Genoveva~Vargas-Solar}
\affG{Univ. Grenoble Alpes, CNRS, Institute of Engineering Univ. Grenoble Alpes (Grenoble INP), LIG, 38000 Grenoble, France and
	French-Mexican Laboratory of Informatics and Automatic Control (LAFMIA), Mexico/France
	\\
  E-mail: genoveva.vargas@imag.fr}

\authorH{\sf Jos\'e-Luis~Zechinelli-Martini}
\affH{Universidad de las Am\'ericas-Puebla -- Cholula, Mexico and
	French-Mexican Laboratory of Informatics and Automatic Control (LAFMIA), Mexico/France\\
  E-mail: joseluis.zechinelli@udlap.mx}

@@

\REF{to this paper should be made as follows: Khalid Belhajjame, Valeria~de~Castro, Javier~A.~Espinosa-Oviedo, Martin~A.~Musicante, Umberto~Souza~da~Costa, Pl\'acido~A.~Souza~Neto, Genoveva~Vargas-Solar, Jos\'e-Luis~Zechinelli-Martini (xxxx) `\pisodm: Building SOC Applications in the Presence of Non-Functional Requirements', {\it International Journal of Web and Grid Services}, Vol. x, No. x, pp.xxx\textendash xxx.}

\begin{bio}
Khalid Belhajjame is a lecturer (Maitre de Conf\'erences) at the University Paris-Dauphine, where he is a member of the LAMSADE. His research interests lie in the areas of information and knowledge management. He has made key contributions to the areas of pay-as-you data integration, e-Science, scientific workflow management, provenance tracking and exploitation, and semantic web services.
\vs{9}

@@

\noindent Javier Alfonso Espinosa-Oviedo is a computer scientist specialized in the domains of databases and distributed systems. His research focuses mainly on large-scale data management and processing based on service oriented architectures. He currently works as postdoctoral researcher at the Barcelona Supercomputing Centre (BSC), in the Extreme Computing Group, and is researcher at the French-Mexican Laboratory of Informatics and Automatic Control (LAFMIA), in the Database Management Group. His research interests include: Stream Processing, Urban Computing, Digital Humanities, Data Visualization. He has participated in several national and European projects (CASES EU-FP7; S2EUNET FP7-IRSES; POLIWEB PEPS CNRS), and has been invited as visiting researcher in different institutions (POLITO, Italy; UdelaR, Uruguay; NUAA, China; UDLAP, Mexico) where he has lectured on selected topics of data management.
\vs{9}

\noindent Martin A. Musicante received his B.Sc at ESLAI, Argentina, in 1988 and his M.Sc and PhD in Computer Science at Universidade Federal de Pernambuco, Brazil, in 1990 and 1996, respectively. He is full professor at Universidade Federal do Rio Grande do Norte-UFRN (Natal, Brazil). He is part of the graduate program in Computer Science at UFRN. Martin was associate researcher at LI - Universit\'e Fran\c{c}ois Rabelais Tours (2002-2011) and at LIFO - Universit\'e d'Orl\'eans, France, since 2008. 
\vs{9}

@@

\noindent Pl\'acido~A.~Souza~Neto received his B.Sc at CEFET-RN, Brazil, in 2005 and his M.Sc and PhD in Computer Science at Universidade Federal de Rio Grande do Norte, Brazil, in 2007 and 2012, respectively. He is an associate professor at Instituto Federal do Rio Grande do Norte-IFRN (Natal, Brazil). He was part of LIG (Grenoble - France) between 2014-2015 for as a post-doc fellow. He is part of the graduate program in Software Analysis and Development at IFRN. Pl\'acido~A.~Souza~Neto's main current research topics are Software Engineering, Data Analysis, Model Driven Development and Web Services.
\vs{9}

@@

\noindent Jos\'e-Luis~Zechinelli-Martini is titular professor of the Department of Computing, Electronics and Mecatronics at the Universidad de las Américas Puebla (UDLAP) since 2002 and he is currently senior researcher at LAFMIA. He is head of the Data and Knowledge Management Group (DBKM) of LAFMIA. In 2001 he obtained his Ph.D. in Computer Science and in 1997 he obtained his Master Degree in Computer Science at University Joseph Fourier, Grenoble, France. In 1993 he obtained his diploma on Computer Systems Engineering at UDLAP. Between 2003 and 2006 he was director of the CENTIA and head of the PhD program on Computer Science. His research project concerns on the integration of Big Data collections on different infrastructures and the specification of spatio-temporal and visualization query languages for retrieving multimedia and multiform data from distributed services.
\end{bio}

@@

\begin{compactenum}[i.]
\item To improve the development process by providing an abstract view of the application and helping to ensure the conformance to its specification.
\item To reduce the programming effort through the semi-automatic generation of  models for the application,  to produce concrete implementations from higher-level models.
\item To provide a general way of describing non-functional requirements.
\end{compactenum}

The applicability of our proposal was tested with an industrial case study concerning risk assessment for financial companies as implemented by the ORCA System\footnotemark \footnotetext{The ORCA System is a trademark of GCP Global (www.gcpglobal.com).}. In this work we show the application of our method \pisodm to develop a service based application called \FlyingPig that provides risk assessment as a service.
The models presented here were generated as a result of interacting with software developers at GCP Global and trying to fulfill  all the non-functional requirements present in the application.

@@

Despite the different notations found in the literature for classifying NFRs, some NFRs are frequently considered, such as \textit{security}, \textit{performance}, \textit{reliability}, \textit{usability}, and \textit{availability}.
However, distinct hierarchies and models are proposed for NFRs, according to different perspectives.
We have identified a number of approaches~\cite{DAmbrogio06,CholletL09,SchmelingCM11,BasinDL06,Fabra2011,OvaskaEHPA10} that use MDD (Model Driven Development) for designing and developing applications.

@@

Figure~\ref{fig:CIM:usecasemetamodel} shows the \textit{$\pi$-UseCase} meta-model.
This model is  used to give the first representation of the application in terms of functionality, and of its non-func\-tion\-al requirements.
The notion of \textit{policy} is used to describe NFRs.
Figure~\ref{fig:CIM:usecasemetamodel} highlights the concepts related to NFRs.
The \textit{$\pi$-UseCase} meta-model extends the UML Use Case meta-model to describe NFRs with  the following  concepts:  \textsc{Business service}\footnotemark \footnotetext{We use the 
{\sc small caps} font for referring to classes of a meta-model.}, {\sc End consumer}, {\sc Requirement}, {\sc Use Case}, {\sc Composite Use Case}, {\sc Non-\-Func\-tion\-al Requirement}, {\sc Non-Functional} {\sc At\-tri\-bute} and {\sc Constraint}.
An {\sc End Consumer} is represented by an {\sc Actor}.
An  {\sc Actor} is related to {\sc Use Cases} (from the original UML definition), as a {\sc  Composite Use Case} is a set of actions performed by the system which can be broken into different {\sc Use Cases}.
{\sc  Business Service} aggregates several {\sc Use Cases},  a service can be expressed by one or more use cases.
 The {\sc Business Collaborator} concept is represented  by {\sc Packages}.
A {\sc Business Collaborator} denotes an external service or a system that interacts with the application that is being modelled.
Each {\sc Business Collaborator} combines the features described in each  {\sc Package}.
%Thus, the service functions can be specified as being grouped into packages.

@@

\begin{example}[To Publish Music \textit{(cont)}]\label{ex:toPublicMusic3}
Considering the example scenario, the contract based process of activities  is shown in Figure~\ref{fig:CIM:serviceprocess}. The buy music and publish music services (update Twitter and Facebook) have pre- and post-conditions assertions that are composed into a contract for each service. The buy music pre-conditions consist in verifying:
\textit{(i)} if the User data are correct;
\textit{(ii)} if the User is already logged in Spotify;
\textit{(iii)} if bank account information is correct and;
\textit{(iv)} if there are enough funds in the bank account to cover the payment.
A post-condition ensures the complete transaction and verifies if a notification about the payment authorization was sent both to the user and to Spotify. 
There are four assertions for the buy music action, and each assertion has been detailed with the assertion property and predicate that must be verified. 
To update services, depending on each service, there may be different restrictions. As an example, a new verification of user data and message format is appropriate (maximum 140 characters), in the case of Twitter. In the case of Facebook, it is required that the user is already logged in Spotify and these data are the same as Facebook.
As post-condition, the application ensures that the Facebook service sends a notification of success.
To update Twitter a pre-condition is required, while to update Facebook it is necessary to check a pre-condition and a confirmation notice (modeled as post-condition).
As a pre-condition for ``twitter update'' it is necessary that (i) the music format is correct and (ii) the twitter login and password are correct for the update.
\end{example}

@@

\item The {\sc ServiceActivity} meta-class represents classes of composite activity types that must be carried out as part of a business service,  composed of  execu\-ta\-ble nodes.

@@

The relationships of type  {\sc Extend} and {\sc Include}  determine the way the business process is expressed as a workflow.  
The generated workflow is composed of {\sf Fork} and {\sf Join} nodes,  {\sc Control flow} constructors, as well as entities of type {\sc Action}.

@@

Figure~\ref{fig:E3valuemodel} shows the value model for the \FlyingPig\ application.
It is a business model that graphically represents a business case as a set of value exchanges ($\triangleright$ and $\triangleleft$) and value activities (rounded boxes) performed by business actors (squared boxes).
We identify two business actors: \textsl{ORCA} and \textsl{Broker}.
Brokers emit requests for risk assessment for one or more companies.
ORCA has two value activities which are services that provide an economical benefit:  \textsl{Identify Amendments} and \textsl{Assess Risk Situation}.
The values exchanged between ORCA and the brokers are:
\textit{(i)} \textsl{Questionnaire and Evidence} filled with information about the client company;
\textit{(ii)} \textsl{Amendments} which are ORCA's rec\-om\-men\-da\-tions, based on the data provided by the answers to questionnaires;
\textit{(iii)} \textsl{Evaluation Reports} for the client companies;
and
\textit{(iv)} the risk assessment \textsl{fee}.
%
The dependency path in Figure~\ref{fig:E3valuemodel} initiates with the need of assessment emitted by a particular company.
Once this need has been declared, the value exchanges between ORCA and Broker are triggered.
The client company provides ORCA with information (answers to a questionnaire), evidence (to support the information) and a fee (monetary value).
In the next step, ORCA suggests amendments (recommendations to change practices) and provides an evaluation report.

@@

Figure~\ref{fig:BPMNmodel} shows the BPMN model
for the \FlyingPig\ scenario. This model is partitioned for better understanding the value exchanging process.
The model includes two pools representing the \textsl{ORCA} system and the \textsl{Brokers}.
Brokers have two lanes, the client \textsl{Company} and a \textsl{User}.
The user is a contact member of the company, who  coordinates the assessment process.
This process  involves other members of the company as well.
%
The risk assessment process starts after a request from a company.
This corresponds to the value model, in which the start stimulus triggers the whole process.
The request leads to the definition of a group of users that will answer questionnaires to evaluate risk.
Other tasks include amending a ``risky situation'' as well as producing evidence to show that a specific risk has been eliminated\footnotemark \footnotetext{Risky situations include  material facts such as not facilitating access to physically disabled people in a bank agency or having an unsecured access to the premises of the company.
They can be also immaterial restrictions such as the protocol used for accessing data on the company's computer server.}.

@@

\begin{compactenum}
\item An acknowledgement is due in less than 30 seconds after registering a task or demand for assessment.
\item The system should be able to deal with, at least, 200 users.
\item If the number of requests exceeds 200, \FlyingPig\ should implement a load balance strategy for processing the requests.
\item The privileges of the Channel-Broker must be verified \textit{before} the execution of the actions associated to the \textsf{designate user in charge} $\pi$-use case.
\item The privileges of users must be verified \textit{before} the execution of the actions associated to the \textsf{answer questionnaire and add evidence} $\pi$-use case.
\item All questionnaires need to be fully answered in order to consider a task as completed.
\item There is a time limit (in days) for amendments required by the system.
\end{compactenum}

@@

\section*{Acknowledgements}
This research has been partially financed by the Government of the Autonomous Community of Madrid under the SICOMORo-CM project (S2013/ICE-3006), and by the ELASTIC project (TIN2014-52938-C2-1-R), financed by the Spanish Governments Ministry of Science and Innovation. 
This work is partially supported by INES, grant CNPq/465614/2014-0 (Brazil).
